Automatic Hadith Graphs using Arabic Morphological Analysis

### 2011-06-02 tex/hadith.ijcnlp.tex
results section draft written

%\newcommand{\CharCodeIn}[1]{`\CodeIn{#1}'}
\newcommand{\CodeIn}[1]{{\small\texttt{#1}}}
\newcommand{\frl}[1]{\fbox{\RL{#1}}} 
\newcommand{\noArRL}[1]{\arabfalse\RL{#1}\arabtrue} 
\newcommand{\noTrRL}[1]{\transfalse\RL{#1}\transtrue}

@@

To evaluate our approach, we performed experiments on three books of 
hadith~\cite{IbnHanbal,AlTousi,AlKulayni} whose accuracy results are detailed in 
Tables~\ref{t:hadithresults} and \ref{t:nopunctlearnresults}. We used recall and precision as our evaluation metrics.
We report results on three levels of accuracy: segmentation, sanad boundary and
narrator boundary. Segmentation accuracy refers to the success of NaGEMA in
detecting in the plain text of a hadith book the locations of the different
narrations that it contains. While the sanad boundary is a measure of the accuracy
in reporting the correct number of narrators in the sanad. Finally, the narrator boundary refers
to the accuracy in reporting the correct number of words inside each narrator.

Precisely defined, segmentation recall refers to the fraction of extracted narrations from 
those which are correct; and segmentation precision refers to the fraction of correct narrations
from those extracted. Similarly, sanad boundary recall is a measure whether we detected all narrators
in the sand; and precision is a measure whether we did so without introducing much false positives.

iTree does not tackle the problem hadith segmentation. In contrast to NaGEMA, it does not work on a book level, 
instead it assumes that the knowledge of what part of the text of a hadith book is a narration is available.
Consequently, for the narrators to be extracted, the hadith must be manually extracted
from the book and inputted on its own to the tool. Still however, in many cases it does not recognize the structure of
the inputted hadith and is incapable of extracting any useful information from the narration. 
In table~\ref{t:hadithresults}, we report the fraction of narrations which iTree recognizes from those inputted, instead
of the segmentation measure used for NaGEMA. This measure is equivalent to the concept of recall; nonetheless, precision
in this context is not applicable since by default the input is required to be represent correctly extracted narrations.

Now we move to explain the significance of the experiments performed.

@@

We ran our experiments using a dual core 2.66 Ghz 64-bit processor 
with 4GB of memory using a Linux operating system. 
We report our results in Table~\ref{t:hadithresallresults} on the 
three hadith books.
NaGEMA detected narrator chains and segmented the books 
correctly with a chain accuracy above 97\% and a narrator name
accuracy above 90\%
in all cases and across all the 1986 traditions in the three 
different books with different formats.

The row ``word count'' is an indicator of the size of the data.
The %numbers in 
rows ``names'', ``narrators'', and ``chains'' denote the total
number of the corresponding entities per book.
The row ``ignored names'' reports the number of names detected 
outside the chains and thus are irrelevant to
the application. 
%In addition, the rows ``names/narrator'' and ``narrators/chain'' 
%report the average
%number of names per narrator and 
%the average number of narrators per chain respectively.

The ``segmentation accuracy'' reports on the accuracy of 
segmentation of the book into separate hadiths.
We computed the metric manually by marking the beginning 
and end of a representative sample of hadiths in each 
book and compared that to the NaGEMA results. 
We used the same approach to compute all other accuracy measures.
The ``chain accuracy'' reflects the percentage of correct narrators 
covered by extracted chains.
The ``narrator name accuracy'' row reflects the percentage of 
correct proper names detected within
narrator structures.

%The row ``name false positives'' reports the percentage of words 
%recognized as names while they should not.
%We notice that this metric did not affect the accuracy
%of narrator and chain segmentation since detecting
%a narrator or a chain with the refined analysis without substantially affecting the 
%high abstract measures such as chain and segmentation
%accuracy.

@@

The closest to our work is e-Narrator~\cite{Azmi2010}, a 
tool that uses a grammar based approach to solve 
the narrator extraction problem. 
The e-Narrator tool preprocesses the text to remove 
punctuation and diacritics and to normalize white
spaces. 
Then e-Narrator uses a similarity-based approach
to memory based learning~\cite{Azmi2010} in order to perform 
shallow parsing of the preprocessed text. 
The e-Narrator tool uses a parser based on a context
free grammar that enumerates several ways to express
the name of the prophet, several possible words that 
might precede the name of the prophet, several possible
words that might separate two narrators, and several
words that might separate parts of the name of the narrators.
The e-Narrator tool fails when a variation of one of the 
listed words and not an exact form of it
happens in the text. 
In their grammar they consider a name to be any sequence of 
legal Arabic characters. 
The e-Narrator tool generates successfully 86.7 percent of
the narration chains of 90 selected traditions with 
34 simple cases and 56 hard cases.

>>>>

%\newcommand{\CharCodeIn}[1]{`\CodeIn{#1}'}
\newcommand{\CodeIn}[1]{{\small\texttt{#1}}}
\newcommand{\frl}[1]{\fbox{\RL{#1}}} 
\newcommand{\noArRL}[1]{\arabfalse\RL{#1}\arabtrue} 
\newcommand{\noTrRL}[1]{\transfalse\RL{#1}\transtrue} 
\newcommand{\noTrnoVocRL}[1]{\transfalse\novocalize\noTrRL{#1}\vocalize\transtrue}  
\newcommand{\noVocRL}[1]{\transtrue\novocalize\RL{#1}\vocalize}

@@

To evaluate our approach, we performed experiments on three books of 
hadith~\cite{IbnHanbal,AlTousi,AlKulayni} whose accuracy results are detailed in 
Tables~\ref{t:hadithresults} and \ref{t:nopunctlearnresults}. 
The numbers we present in the tables are the result of a manual verification of the correctness of the outputs of the first
10\% of the narrations in the books under consideration.

We used recall and precision as our evaluation metrics.
We report results on three levels of accuracy: segmentation, sanad boundary and
narrator boundary. Segmentation accuracy refers to the success of NaGEMA in
detecting in the plain text of a hadith book the locations of the different
narrations that it contains. While the sanad boundary is a measure of the accuracy
in correctly reporting the individual narrators inside the sanad. Finally, the narrator boundary refers
to the accuracy in correctly reporting the words that constitute the narrators.

Precisely defined, segmentation recall refers to the fraction of the narrations correctly detected to the
total number of narrations available; while segmentation precision refers to the fraction of correctly detected narrations
from those extracted. Similarly, sanad boundary recall is a measure whether we detected all narrators
in the sand; while precision is a measure whether we did so without introducing much false positives. 
The same concepts apply to the level of narrator boundary where the count is of the number of words which constitute a valid narrator.

iTree does not tackle the problem hadith segmentation. In contrast to NaGEMA, it does not work on a book level, 
instead it assumes that the knowledge of which part of the text of a hadith book is a narration is available.
Consequently, for the narrators to be extracted from the sanad of a narration, the hadith must be manually extracted
from the book and inputted on its own to the tool. Still however, in many cases it does not recognize the structure of
the inputted hadith and is incapable of extracting any useful information from the narration. 
In table~\ref{t:hadithresults}, we report the fraction of narrations which iTree recognizes from those inputted, instead
of the segmentation measure used for NaGEMA. This measure is equivalent to the concept of recall; nonetheless, precision
in this context is not applicable since by default the input is required to be represent correctly extracted narrations.

In those experiments, we were interested in evaluating the approaches used by iTree and NaGEMA, without any bias that results
from the difference in the coverage of the lexicons used. For this reason, we appended the list of names used by iTree with those
available in Sarf's lexicon on top of which NaGEMA operates.

Now we move to explain the significance of the experiments performed. First, we compare the recall of the segmentation 
in NaGEMA and that of hadith acceptance rates in iTree. Although the task of segmentation is more complex than that of
hadith recognition/acceptance, we still notice that iTree has on the average 35.7\% recall rate compared to 99.9\% for 
NaGEMA. However, we notice that the difference in these numbers depended highly on the books under consideration. For instance,
for the book of musnad, both approaches correctly detected  practically all narrations under consideration; 
however iTree suffers a lot in 
the books of both Kafi and Istibsar , resulting in a recall of less than 5\%. This is due to the less structured nature of the narrations
those books contain. For example, iTree's grammar is defined such that a hadith starts by an Ikhbar word (\noVocRL{AdaT al-A_hbAar}) such as
\noVocRL{qAl}, \noVocRL{.hadda_t}, etc...; 
however, those books had a more flexible style of expressing the narration 
and most of them started directly by narrator name without a preceeding Ikhbar word. This is a strong evidence of the supperiority of 
our tolerance-based state-machine compared to the strict grammar approach used in iTree. 
Clearly, our machine does not fail on such cases, since what it detects as a hadith is based on a concentration of names intervened by narrator 
connectors. Similarly, iTree had a lower sanad boundary precision (62.4\% on the average) due to the fact that the its grammar has no method
of detecting that the hadith ended except if it reaches a prophet indicative phrase such as \noVocRL{rasowl al-lah}, 
\noVocRL{.sal_A `alayh al-lah wasalam}, etc.. However, especially in the books of Kafi and Istibsar, the prophet is not explicitly mentioned but 
implicitly understood. In those cases, iTree will continue reporting narrators whenever it reaches a word that can act as a name even if it appears
in the matn of the hadith. On the other hand, NaGEMA considers that a sanad ends whenever a tolerance state is broken even if it does not reach a prophet
indicative phrase. Narrator boundary accuracy was similar however for both approaches because they relied on the same name lexicons.

@@

After having provided evidence to the superiority of our approach compared to that of iTree, 
we move to inspect the effect of two of the optimizations we implemented in NaGEMA.
Those optimizations are: utilizing punctuation in disambiguating narration detection and narrator boundaries, 
and learning names of narrators based on their local context.
In Table~\ref{t:nopunctlearnresults}, we report the results of running NaGEMA, 
disabling each of the optimizations at a time.

We notice that punctuations are useful for increasing all precision measures: hadith segmentation, sanad boundary and
narrator boundary. Those measures are enhanced by about 3\%, 2\%, 1\% respectively as punctuation related information is 
utilized.  Clearly, punctuation can help eliminate any confusion that may result from a concentration of names and words that are
can be interpreted shallowly as narrator connectors. It also helps cleaning the sanad of a narration from names that coincidently appear at the 
end of the matn of a previous narration. If close enough those names can be assumed as narrators in the sanad at hand; however, punctuation marks
reduce such confusions.

Concerning the ability to learn names, our results show that it enhances mainly the recall of sanad boundaries by about 3.4\% on the average.
Such an increased accuracy although small is not insignificant, since the task of hadith authentication requires a high accuracy. In particular,
sometimes the presence of a specific narrator in the chain can render a hadith as not trustworthy since the narrator is not considered credible.
That's why it is important not to lose any of the narrators that appear in the sanad.

@@

The closest to our work is e-Narrator~\cite{eNarrator}, a 
tool that uses a grammar based approach to solve 
the narrator extraction problem. 
The e-Narrator tool preprocesses the text to remove 
punctuation and diacritics and to normalize white
spaces. 
Then e-Narrator uses a similarity-based approach
to memory based learning~\cite{eNarrator} in order to perform 
shallow parsing of the preprocessed text. 
The e-Narrator tool uses a parser based on a context
free grammar that enumerates several ways to express
the name of the prophet, several possible words that 
might precede the name of the prophet, several possible
words that might separate two narrators, and several
words that might separate parts of the name of the narrators.
The e-Narrator tool fails when a variation of one of the 
listed words and not an exact form of it
happens in the text. 
In their grammar they consider a name to be any sequence of 
legal Arabic characters. 
The e-Narrator tool generates successfully 86.7 percent of
the narration chains of 90 selected traditions with 
34 simple cases and 56 hard cases.
